Relative parabolic factorizations of Chevalley groups

### 2015-09-06 paper.tex
Reordering and fixes in sec:elementary

@@

\begin{rem}
Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.
\end{rem}
For other classical root systems the elementary root unipotents are as follows.

In case $\Phi=\rC_\ell$ the long and short root unipotents are
\begin{align*}
& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
\end{align*}

Here $\varepsilon_i$ is the sign of $i$.

In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
\begin{align*}
& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
\end{align*}

The following result of H.~Matsumoto describes the action of elementary root unipotents in a basic representation of $\G(\Phi, R)$.
\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
 Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
 One can choose a basis $v_\lambda$, $\lambda\in\Lambda(\pi)$ of $V$ such that the action of elementary root unipotents $t_\alpha(\xi)$ on it is described by the following formulae:
 \begin{thmlist}
  \item $t_{\alpha}(\xi) v_\lambda = v_\lambda$ for $\lambda\in\Lambda^*(\pi), \lambda+\alpha\not\in\Lambda(\pi)$;
  \item $t_\alpha(\xi)v_\lambda=v_\lambda\pm\xi v_{\lambda+\alpha}$ for $\lambda,\lambda+\alpha\in\Lambda^*(\pi)$;
  \item $t_\alpha(\xi)v_0 = v_0$ for every $v_0\in V^0$, $\alpha\not\in\Lambda^*(\pi)$;
  \item $t_\alpha(\xi)v_{-\alpha}=v_{-\alpha}\pm\xi v_0(\alpha)\pm\xi^2 v_{\alpha},$ $t_\alpha(\xi)v_0 = v_0\pm\xi\alpha_*(v_0)v_\alpha$ for $\alpha\in\Lambda^*(\pi)$.
 \end{thmlist}
\end{lemma}

>>>>

The following result of H.~Matsumoto describes the action of elementary root unipotents in a basic representation of $\G(\Phi, R)$.
\begin{lemma}[{\cite[Lemma~2.3]{Ma69}}]\label{lemma:Matsumoto}
Let $(V, \pi)$ be a basic representation of $\G(\Phi, R)$.
One can choose a basis $v^\lambda$, $\lambda\in\Lambda(\pi)$ of $V$ such that the action of the elementary root unipotents $x_\alpha(\xi)$ on it is described by the following formulae:

\begin{tabular}{ll}
If $\lambda\in\Lambda^*,\ \lambda+\alpha\notin\Lambda$, then & $x_\alpha(\xi)v^\lambda=v^\lambda$; \\
If $\lambda,\lambda+\alpha\in\Lambda^*$, then & $x_\alpha(\xi)v^\lambda=v^\lambda\pm\xi v^{\lambda+\alpha}$; \\
If $\alpha\notin\Lambda^*$, then & $x_\alpha(\xi)v^0=v^0$ for any $v^0\in V^0$; \\
If $\alpha\in\Lambda^*$, then & $x_\alpha(\xi)v^{-\alpha}=v^{-\alpha}\pm\xi v^0(\alpha)\pm\xi^2 v^\alpha$ and \\
& $x_\alpha(\xi)v^0=v^0\pm\xi\alpha_*(v^0)v^\alpha$.
\end{tabular}
% \begin{thmlist}
%  \item $x_{\alpha}(\xi) v_\lambda = v_\lambda$ for $\lambda\in\Lambda^*(\pi), \lambda+\alpha\not\in\Lambda(\pi)$;
%  \item $x_\alpha(\xi)v_\lambda=v_\lambda\pm\xi v_{\lambda+\alpha}$ for $\lambda,\lambda+\alpha\in\Lambda^*(\pi)$;
%  \item $x_\alpha(\xi)v_0 = v_0$ for every $v_0\in V^0$, $\alpha\not\in\Lambda^*(\pi)$;
%  \item $x_\alpha(\xi)v_{-\alpha}=v_{-\alpha}\pm\xi v_0(\alpha)\pm\xi^2 v_{\alpha}$,\\
%   $x_\alpha(\xi)v_0 = v_0\pm\xi\alpha_*(v_0)v_\alpha$ for $\alpha\in\Lambda^*(\pi)$.
% \end{thmlist}
\end{lemma}

\begin{rem}
Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ (for some choice of $\lambda_1,\lambda_2$) instead of $x_{\lambda_1-\lambda_2}(\xi)$.
For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. This is done in order to fix the signs in \cref{lemma:Matsumoto}.
\end{rem}
For classigal groups there is a standard way to fix the signs.
In case $\Phi=\rC_\ell$ the long and short root unipotents are
\begin{align*}
& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
\end{align*}
Here $\varepsilon_i$ is the sign of $i$.
In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
\begin{align*}
& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
\end{align*}

@@
